PANCHANGE_analysis

### 2020-12-17 PANCHANGE_analysis.Rmd
added paired ttests for sum scores

## Forest plots
### disorder
```{r forest plot by disorder prepan, fig.height=30, fig.width=35, dpi=120}

@@

```{r forest plot by disorder retro, fig.height=30, fig.width=30, dpi=120}

@@

### disorder (no PCL)
```{r forest plot by disorder prepan no pcl, fig.height=30, fig.width=30, dpi=120}

@@

```{r forest plot by disorder retro no pcl, fig.height=30, fig.width=30, dpi=120}

@@

### time point 
```{r forest plot by time point gad, fig.height=30, fig.width=30, dpi=120}

@@

```{r forest plot by time point phq, fig.height=30, fig.width=30, dpi=120}

@@

```{r forest plot by time point pcl, fig.height=30, fig.width=30, dpi=120}

@@

```{r forest plot by sample retro only gad, fig.height=30, fig.width=30, dpi=120}

@@

```{r forest plot by sample retro only phq, fig.height=30, fig.width=30, dpi=120}

@@

```{r forest plot by sample retro only pcl, fig.height=30, fig.width=30, dpi=120}

>>>>

## Forest plots
### disorder
```{r forest plot by disorder prepan, fig.height=30, fig.width=50, dpi=120}

@@

```{r forest plot by disorder retro, fig.height=30, fig.width=50, dpi=120}

@@

### disorder (no PCL)
```{r forest plot by disorder prepan no pcl, fig.height=30, fig.width=50, dpi=120}

@@

```{r forest plot by disorder retro no pcl, fig.height=30, fig.width=50, dpi=120}

@@

### time point 
```{r forest plot by time point gad, fig.height=30, fig.width=50, dpi=120}

@@

```{r forest plot by time point phq, fig.height=30, fig.width=50, dpi=120}

@@

```{r forest plot by time point pcl, fig.height=30, fig.width=50, dpi=120}

@@

```{r forest plot by sample retro only gad, fig.height=30, fig.width=50, dpi=120}

@@

```{r forest plot by sample retro only phq, fig.height=30, fig.width=50, dpi=120}

@@

```{r forest plot by sample retro only pcl, fig.height=30, fig.width=50, dpi=120}
